Blum axioms and nondeterministic computation of functions

### 2016-04-17 paper.tex
paper.tex: Rewrite introduction to section with the four definitions.

This section surveys four approaches
for defining nondeterministic computation of functions.
Sections \ref{sec:godel-numberings} and~\ref{sec:blum-axioms}
can be understood as ``quality requirements''
for the definitions;
that is, the definitions will need to be translatable as
acceptable Gödel numberings,
and the ``natural'' extension of space and time complexity
must satisfy Blum axioms.

>>>>

This section surveys four approaches
for defining nondeterministic computation of functions.

Sections \ref{sec:godel-numberings} and~\ref{sec:blum-axioms}
introduced the concept of acceptable Gödel numbering,
the Blum axioms,
and its complexity classes.
As we want to regard these concepts as ``quality requirements''
for the definitions,
we will analyze each of them to see whether they define acceptable Gödel numberings,
the analogous time complexity defines a Blum complexity measure,
and that the characteristic function of the Boolean satisfiability problem
can be solved in ``polynomial time'' according to that complexity measure.
